Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-07-16 ltx/data_paper/DataPaper.tex
edits to discussion

The additional Taylor expansion step inroduced in the E-step resembles the extended Kalman filtering (EKF) \cite{Jazwinski1970,Chui2009} in which a stationary nonlinear dynamic system is approximated by a linear non-stationary system using the first order Taylor approximation of the state and observation equations about the state estimates and then applying regular Kalman filter to the linear system. This may suggest that the extended Kalman smoother is a natural approach to infer the sequence of states in the presented framework. However, extended Kalman smoother (EKS) requires relinearising about the backwards estimates which in turn necessitates the nonlinear mapping to be uniquely invertible. Although this is indeed the case in the neural field equation employed in this work it will impose more computational complexity in the state estimation procedure. In addition, URTSS provides better approximation compared to the EKS and therefore the approximated lower bound will be more accurate \cite{Haykin2001}.

>>>>

The additional Taylor expansion step inroduced in the E-step resembles the extended Kalman filtering (EKF) \cite{Jazwinski1970,Chui2009} in which a stationary nonlinear dynamic system is approximated by a linear non-stationary system using the first order Taylor approximation of the nonlinear equations about the state estimates. This may suggest that the extended Kalman smoother is a natural approach to infer the sequence of state vecors in the presented framework. However, extended Kalman smoother (EKS) requires relinearising about the backwards estimates which in turn necessitates the nonlinear mapping to be uniquely invertible. Although this is indeed the case in the neural field equation employed in this work it will impose more computational complexity in the state estimation procedure. In addition, URTSS provides better state approximation compared to the EKS \cite{Haykin2001} and therefore the approximated lower bound will be more accurate  resulting in better parameter estimations.
